brados: declarative, programmable object storage

### 2016-05-25 paper.tex

\begin{enumerate}
    \item {\bf Entry addressing.} We refer to the method by which a client
        locates a log entry in Ceph as entry addressing, and we consider two
        strategies. In a one-to-one (1:1) strategy each log entry is stored in
        a distinct object with a name derived from the associated log entry
        position. This is an attractive option because it is trivial for
        clients to locate a log entry given its position.  In contrast, an N:1
        strategy \emph{stripes} log entires across a smaller set of objects,
        but this adds complexity to both the client and the object interface which
        must multiplex a set of entries.

@@

We consider two high-level design prototypes in this paper based on both the
key-value and bytestream interfaces. The summary of performance of these
designs is shown in Figure~\ref{fig:cls_wr_jewel} where we begin by
highlighting two baseline throughputs labeled \emph{librados} and
\emph{cls\_null} that correspond to the baseline append throughput described
in the previous section, and the append throughput achieved with \emph{object
class} overhead included. We will discuss the performance of our two prototype
designs relative to the base cost of using \emph{object class} facility.

The first design is based on the key-value interface. In this design the epoch
value is stored under a fixed key, and the metadata associated with each log
entry is stored under a key derived from the log position. The expected throughput of
this design is shown in Figure~\ref{fig:cls_wr_jewel} and labeled as
\emph{cls\_full\_omap}. This result shows us that even for very small values
the cost of managing data in the key-value store introduces significant
overhead. In contrast, the unstructured bytestream interface imposes little
to no restriction on how it is used.

An obvious choice for encoding the singleton epoch value in the bytestream is
to position it at a fixed offset such as in a header. A method for indexing
entry metadata is far less obvious. Solutions span a wide design spectrum and
include approaches such as encoding a search tree into the bytestream, or
exploiting the regularity log addressing and storing a dense array that can be
efficiently indexed. While there is clearly a wide variety of approaches, we
have chosen to examine the overhead incurred by an hypothetical best-case
design in which per-entry metadata can be accessed with a single I/O. The I/O
overhead of the test includes (1) read epoch value from a fixed header
location, (2) read the per-entry metadata, and in the case of an update (3)
write the updated per-entry metadata. The expected throughput from such a
design is shown in Figure~\ref{fig:cls_wr_jewel} labeled as
\emph{cls\_full\_hdr} and performs with roughly a 6\% overhead.

@@

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context. To illustrate these contexts, we describe the
software, system tunable, and hardware parameters that affect the performance
of our CORFU implementation. The complexity and breadth of our parameter sweep,
and the fact that our state space grew so large, motivates brados in section 4.

@@

Ceph releases stable versions every year (Oct/Nov) and LTS versions every 3-4
months~\cite{website:ceph-releases}. The head of the master branch moves
quickly because there are over 400 contributors and an active mailing list.
Over the past calendar year, there were between 70 and 260 commits per
week~\cite{website:ceph-github}.

@@

This many domain-specific tunables makes it almost impossible to come up with
the best set of tunables, although auto-tuning like the work done
in~\cite{behzad:sc2013-autotuning} could go a long way. Regardless of the
technique that we use, it is clear the the number of tunables increases the
physical design parameters to an unwieldy stae space size.

\textbf{Takeaway}: the number and complexity of Ceph's tunables make
brute-force parameter selection impossible.

>>>>

\begin{enumerate}
    \item {\bf Entry addressing.} We refer to the method by which a client
        locates a log entry in Ceph as entry addressing, and we consider two
        strategies. In a one-to-one (1:1) strategy each log entry is stored in
        a distinct object with a name derived from the associated log entry
        position. This is an attractive option because it is trivial for
        clients to locate a log entry given its position.  In contrast, an N:1
        strategy \emph{stripes} log entries across a smaller set of objects,
        but this adds complexity to both the client and the object interface which
        must multiplex a set of entries.

@@

We consider two high-level design prototypes in this paper based on both the
key-value and bytestream interfaces. The summary of performance of these
designs is shown in Figure~\ref{fig:cls_wr_jewel} where we begin by
highlighting two baseline throughputs labelled \texttt{librados} and
\texttt{write only} that correspond to the baseline append throughput described
in the previous section, and the append throughput achieved with \emph{object
class} overhead included. We will discuss the performance of our two prototype
designs relative to the base cost of using \emph{object class} facility.

The first design is based on the key-value interface. In this design the epoch
value is stored under a fixed key, and the metadata associated with each log
entry is stored under a key derived from the log position. The expected
throughput of this design is shown in Figure~\ref{fig:cls_wr_jewel} and labeled
as \texttt{KV}. This result shows us that even for very small values the cost
of managing data in the key-value store introduces significant overhead. In
contrast, the unstructured bytestream interface imposes little to no
restriction on how it is used.

An obvious choice for encoding the singleton epoch value in the bytestream is
to position it at a fixed offset such as in a header. A method for indexing
entry metadata is far less obvious. Solutions span a wide design spectrum and
include approaches such as encoding a search tree into the bytestream, or
exploiting the regularity log addressing and storing a dense array that can be
efficiently indexed. While there is clearly a wide variety of approaches, we
have chosen to examine the overhead incurred by an hypothetical best-case
design in which per-entry metadata can be accessed with a single I/O. The I/O
overhead of the test includes (1) read epoch value from a fixed header
location, (2) read the per-entry metadata, and in the case of an update (3)
write the updated per-entry metadata. The expected throughput from such a
design is shown in Figure~\ref{fig:cls_wr_jewel} labeled as \texttt{BS} for
bytestream and performs with roughly a 6\% overhead.

@@

So far, we have demonstrated that a design based on an N:1 addressing scheme
that stores both log entries and metadata in the bytestream can provide the
best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context. To illustrate these contexts, we describe the
software parameters, system tunables, and hardware parameters that affect the
performance of our CORFU implementation. The complexity and breadth of our
parameter sweep, and the fact that our state space grew so large, motivates the
language for declarative, programmable object storage described in section 4.

@@

Ceph releases stable versions every year (Oct/Nov) and long-term support (LTS)
versions every 3-4 months~\cite{website:ceph-releases}. The head of the master
branch moves quickly because there are over 400 contributors and an active
mailing list.  Over the past calendar year, there were between 70 and 260
commits per week~\cite{website:ceph-github}.

@@

This many domain-specific tunables makes it almost impossible to come up with
the best set of tunables, although auto-tuning like the work done
in~\cite{behzad:sc2013-autotuning} could go a long way. Regardless of the
technique that we use, it is clear the the number of tunables increases the
physical design parameters to an unwieldy state space size.

\textbf{Takeaway}: the number and complexity of Ceph's tunables makes
brute-force parameter selection hard.
